Title

### 2013-03-27 inc/model_results/lens_charge/lens_charge.tex
fix oblate/prolate gaff (ooops)

In the preceding sections it has already been established that prolate eccentricities are preferred for UEM in general.
When focusing the pulse it can be shown that prolate pulses will also have markedly better performance.

@@

\ref{fig:focus_lens_charge} shows the predicted dynamics of the spatial electron pulse waist (HW1/eM) for prolate pulses under perfect focusing for lenses of two focal lengths; a `long' focal length of 60mm (\ref{fig:focus_lens_charge}\subref{fig:focus_lens_charge_long}) and a `short' focal length of 6.0mm (\ref{fig:focus_lens_charge}\subref{fig:focus_lens_charge_short}).
For both lens strengths, the deleterious effects of space-charge are evident as the number of electrons/pulse $ N $ is increased.
To make an effective comparison, highlighting the effect of space-charge alone, the pulses used are at 20kV velocity with $\Delta E = $ 0.5eV but are not simulated using an accelerator.
The length of the accelerator and the anode lensing would make useful comparison difficult; as such the simulation presented approximates a beam which has been perfectly collimated at the front-focal plane of the lens.

>>>>

In the preceding sections it has already been established that oblate eccentricities are preferred for UEM in general.
When focusing the pulse it can be shown that oblate pulses will also have markedly better performance.

@@

\ref{fig:focus_lens_charge} shows the predicted dynamics of the spatial electron pulse waist (HW1/eM) for oblate pulses under perfect focusing for lenses of two focal lengths; a `long' focal length of 60mm (\ref{fig:focus_lens_charge}\subref{fig:focus_lens_charge_long}) and a `short' focal length of 6.0mm (\ref{fig:focus_lens_charge}\subref{fig:focus_lens_charge_short}).
For both lens strengths, the deleterious effects of space-charge are evident as the number of electrons/pulse $ N $ is increased.
To make an effective comparison, highlighting the effect of space-charge alone, the pulses used are at 20kV velocity with $\Delta E = $ 0.5eV but are not simulated using an accelerator.
The length of the accelerator and the anode lensing would make useful comparison difficult; as such the simulation presented approximates a beam which has been perfectly collimated at the front-focal plane of the lens.

### 2013-03-27 inc/model_results/lens_charge/lens_charge_plot.tex
fix oblate/prolate gaff (ooops)

%TODO fix axes to be more consistent
%TODO add N=1e8 for prolate?

\begin{figure}
  \centering
  \centerline{
    \subfloat[][] {
      \label{fig:focus_long_prolate}
      \begin{tikzpicture}
        \input{lens_60mm_prolate_data}
        \node at (5.9,1.65) {$N=10^5$};
        \node at (4,3) {$N=10^6$};
        \node at (3,4) {$N=10^7$};
      \end{tikzpicture}
    }
    \subfloat[][] {
      \label{fig:focus_long_oblate}
      \begin{tikzpicture}
        \input{lens_60mm_oblate_data}
        \node at (4.2,2.3) {$N=10^5$};
        \node at (3.3,3.5) {$N=10^6$};
      \end{tikzpicture}
    }
  }
  \centerline{
    \subfloat[][] { 
      \label{fig:focus_short_prolate}
      \begin{tikzpicture}
        \input{lens_6mm_prolate_data}
        \node at (6.5,3) {$N=10^7$};
      \end{tikzpicture}
    }
    \subfloat[][] { 
      \label{fig:focus_short_oblate}
      \begin{tikzpicture}
        \input{lens_6mm_oblate_data}
        \node at (6.9,2.6) {$N=10^7$};
        \node at (6,2) {$N=10^6$};
      \end{tikzpicture}
    }
  }
  \caption[AG model simulated focal behavior of perfect magnetic lenses as a function of pulse charge $N$]{
    AG model simulated focal behavior of perfect magnetic lenses as a function of pulse charge $N$.
    All plot's pulses begin at the lens' front focal plane at 20 kV velocity ($c/3$) and have the same volume.
    The left plots (\subref{fig:focus_long_prolate} and \subref{fig:focus_short_prolate}) are prolate shaped, initially HW1/eM width $ 500 \mu \text{m}$ and ellipticiy $ \xi ( 0 ) = 0.1 $.
    The right plots (\subref{fig:focus_long_oblate} and \subref{fig:focus_short_oblate}) are oblate shaped, initially HW1/eM width $ 107.7 \mu \text{m}$ and ellipticiy $ \xi ( 0 ) = 10 $.
    Distance traveled in column is measured relative to the lens at $z=0$, in units of the focal lenth.
    The top plots (\subref{fig:focus_long_prolate} and \subref{fig:focus_long_oblate}) have a longer focal length $f = $ 60mm compared to the bottom plots (\subref{fig:focus_short_prolate} and \subref{fig:focus_short_oblate}) $ f = $ 6.0mm.
    A logarithmic scale is used for comparative clarity.
    Clearly the best performance is achieved for shorter focal lengths and prolate pulses even at higher initial charge densities.
  }
  \label{fig:focus_lens_charge}
\end{figure}

>>>>

%TODO fix axes to be more consistent
%TODO add N=1e8 for oblate?

\begin{figure}
  \centering
  \centerline{
    \subfloat[][] {
      \label{fig:focus_long_oblate}
      \begin{tikzpicture}
        \input{lens_60mm_oblate_data}
        \node at (5.9,1.65) {$N=10^5$};
        \node at (4,3) {$N=10^6$};
        \node at (3,4) {$N=10^7$};
      \end{tikzpicture}
    }
    \subfloat[][] {
      \label{fig:focus_long_prolate}
      \begin{tikzpicture}
        \input{lens_60mm_prolate_data}
        \node at (4.2,2.3) {$N=10^5$};
        \node at (3.3,3.5) {$N=10^6$};
      \end{tikzpicture}
    }
  }
  \centerline{
    \subfloat[][] { 
      \label{fig:focus_short_oblate}
      \begin{tikzpicture}
        \input{lens_6mm_oblate_data}
        \node at (6.5,3) {$N=10^7$};
      \end{tikzpicture}
    }
    \subfloat[][] { 
      \label{fig:focus_short_prolate}
      \begin{tikzpicture}
        \input{lens_6mm_prolate_data}
        \node at (6.9,2.6) {$N=10^7$};
        \node at (6,2) {$N=10^6$};
      \end{tikzpicture}
    }
  }
  \caption[AG model simulated focal behavior of perfect magnetic lenses as a function of pulse charge $N$]{
    AG model simulated focal behavior of perfect magnetic lenses as a function of pulse charge $N$.
    All plot's pulses begin at the lens' front focal plane at 20 kV velocity ($c/3$) and have the same volume.
    The left plots (\subref{fig:focus_long_oblate} and \subref{fig:focus_short_oblate}) are oblate shaped, initially HW1/eM width $ 500 \mu \text{m}$ and ellipticiy $ \xi ( 0 ) = 0.1 $.
    The right plots (\subref{fig:focus_long_prolate} and \subref{fig:focus_short_prolate}) are prolate shaped, initially HW1/eM width $ 107.7 \mu \text{m}$ and ellipticiy $ \xi ( 0 ) = 10 $.
    Distance traveled in column is measured relative to the lens at $z=0$, in units of the focal lenth.
    The top plots (\subref{fig:focus_long_oblate} and \subref{fig:focus_long_prolate}) have a longer focal length $f = $ 60mm compared to the bottom plots (\subref{fig:focus_short_oblate} and \subref{fig:focus_short_prolate}) $ f = $ 6.0mm.
    A logarithmic scale is used for comparative clarity.
    Clearly the best performance is achieved for shorter focal lengths and oblate pulses even at higher initial charge densities.
  }
  \label{fig:focus_lens_charge}
\end{figure}

### 2013-03-27 inc/model_results/shapes/shapes.tex
fix oblate/prolate gaff (ooops)

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:compare_shape_N1}
    \input{shapes_N1}
  }
  \\
  \subfloat[][]{
    \label{fig:compare_shape_N1e6}
    \input{shapes_N1e6}
  }
  \caption[AG simulation of free-space pulse expansion]{
    Transverse (solid) and longitudinal (dashed) dynamics of three example pulses for three length/width ratios ($\xi$). 
    The red lines represent a prolate pulse (a ``pancake'') with $\xi=1/3$, green lines for a spherical pulse with $\xi=1$, and blue for an oblate pulse (a ``cigar'') having $\xi=3$.
    The pulses shown in \ref{fig:compare_shape_N1} all have total charge $N=1$, while in \ref{fig:compare_shape_N1e6} the pulses have $N=10^6$.
  }
  \label{fig:compare_shape}
\end{figure}

@@

%TODO perhaps all of this should be moved back or even cut?
I have shown that a prolate spheroid pulse shape is preferred for UEM, both for generation in SECTION %TODO link to Child law discussion
and in this section for propagation.
Further I have shown in %TODO link to section where I show that initial conditions create shorter pulses than laser
that electron pulses shorter than the laser pulse duration are likely occurances.
Henceforth I shall only consider prolate pulses when a choice of initial pulse shape is possible.

>>>>

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:compare_shape_N1}
    \input{shapes_N1}
  }
  \\
  \subfloat[][]{
    \label{fig:compare_shape_N1e6}
    \input{shapes_N1e6}
  }
  \caption[AG simulation of free-space pulse expansion]{
    Transverse (solid) and longitudinal (dashed) dynamics of three example pulses for three length/width ratios ($\xi$). 
    The red lines represent a oblate pulse (a ``pancake'') with $\xi=1/3$, green lines for a spherical pulse with $\xi=1$, and blue for an prolate pulse (a ``cigar'') having $\xi=3$.
    The pulses shown in \ref{fig:compare_shape_N1} all have total charge $N=1$, while in \ref{fig:compare_shape_N1e6} the pulses have $N=10^6$.
  }
  \label{fig:compare_shape}
\end{figure}

@@

%TODO perhaps all of this should be moved back or even cut?
I have shown that a oblate spheroid pulse shape is preferred for UEM, both for generation in SECTION %TODO link to Child law discussion
and in this section for propagation.
Further I have shown in %TODO link to section where I show that initial conditions create shorter pulses than laser
that electron pulses shorter than the laser pulse duration are likely occurances.
Henceforth I shall only consider oblate pulses when a choice of initial pulse shape is possible.

### 2013-03-27 inc/model_results/spacecharge/spacecharge.tex
fix oblate/prolate gaff (ooops)

This trend is clearly evident in \ref{fig:spacecharge_noacc} which presents the predicted HW1/eM pulse width $\sqrt{2 \sigma_{\smallT}}$ (solid line) and longitudinal length $\sqrt{2 \sigma_{z}}$ (dashed line) as a function of the number of electrons in the pulse after a propagation distance of 15cm.
The pulses are not accelerated but rather start with a velocity of $c/3$ (where $c$ is the speed of light in a vacuum), initial width of 1 mm, HW1/eM pulse duration 1 ps, have the initial momentum chirps $\gamma_{\smallT} = \gamma{z} = 0 $ and momentum uncertainties related to an excess photoemission energy of $\Delta E = $ 0.5 eV.
These naive conditions are needed to isolate the behavior of a propagating pulse from its creation environment.
The simulations, clearly indicate that both the electron beam width and length at the end of the simulation will remain unchanged below about $10^5$ electrons/pulse; that is, global space-charge effects only significantly influence the pulse propagation for pulses having more than $10^5$ electrons/pulse.
In the absence of space-charge effects, the presented prolate pulse shaped pulses should be maintained as such during unforced propagation because the electron pulse divergence and its temporal broadening rate are both proportional to $\Delta E^{1/2}$.

>>>>

This trend is clearly evident in \ref{fig:spacecharge_noacc} which presents the predicted HW1/eM pulse width $\sqrt{2 \sigma_{\smallT}}$ (solid line) and longitudinal length $\sqrt{2 \sigma_{z}}$ (dashed line) as a function of the number of electrons in the pulse after a propagation distance of 15cm.
The pulses are not accelerated but rather start with a velocity of $c/3$ (where $c$ is the speed of light in a vacuum), initial width of 1 mm, HW1/eM pulse duration 1 ps, have the initial momentum chirps $\gamma_{\smallT} = \gamma{z} = 0 $ and momentum uncertainties related to an excess photoemission energy of $\Delta E = $ 0.5 eV.
These naive conditions are needed to isolate the behavior of a propagating pulse from its creation environment.
The simulations, clearly indicate that both the electron beam width and length at the end of the simulation will remain unchanged below about $10^5$ electrons/pulse; that is, global space-charge effects only significantly influence the pulse propagation for pulses having more than $10^5$ electrons/pulse.
In the absence of space-charge effects, the presented oblate shaped pulses should be maintained as such during unforced propagation because the electron pulse divergence and its temporal broadening rate are both proportional to $\Delta E^{1/2}$.
